Formal Verification of Real-Time Data Processing of the LHC Beam Loss Monitoring System: A Case Study

### 2011-04-01 fmics/paper.tex
start minor revisions of sec 4

In this section, we describe our approach to formal verification of the SRS component in BLETC and present the formal model and results.

@@

Our goal is to build a generic model of the SRS structure, and to prove that it satisfies its specification, that it calculates approximate running sums of received count values within acceptable error margins.
Let $\mathsf{RS}\;n$ denote, as in Figure~\ref{fig:srs}, the $n$-th output of the SRS structure, which is supposed to compute a sum of received count values, and let $\mathsf{true\_sum}\;n$ denote this sum.
The multi-layered structure of the SRS and the read delay of each shift register result in the outputs of SRS being delayed from the $\mathsf{true\_sum}$ values.
A sketch of the desired correctness statement is: \[\forall{n} \cdot \, \mathsf{RS}\;n= \mathsf{true\_sum}\; n \pm\text{acceptable error}\]
Although Figure~\ref{fig:srs} suggests that the SRS structure has only twelve outputs  (i.e. $0\leq{n}\leq11$), we obtain a more generic result (that is useful in future upgrades of the system) by proving the correctness of the above statement for all values of $n$.

@@

Prior to defining a formal model of the SRS and the theorems on the model, we developed an informal ``white board"-level argument for why the SRS implements its intended behavior.
The essence of this argument relies on four facts which can be established from the structure of the SRS and some details about timing relationship between layers:
\begin{enumerate}
\item The shift register of each slice (except the first) is updated once the content of the shift register of its previous slice is completely updated.
\item The integration window of a given shift register in a slice (except the first slice) can be decomposed into a sequence of  non-overlapping consecutive segments, $S_1, S_2, \ldots, S_w$ (where $w$ is the width of the shift register) each of which is equal to the size of the integration window of the shift register of the previous slice.
\item After a period of initialization, the values stored in the shift register of a given slice (except the first) are the $w$ outputs of the previous slice, where $w$ is the width of the shift register of this slice.
\item After a period of initialization, the output of each slice is always equal to the sum of the contents of its shift register.
\end{enumerate}

>>>>

In this section, we describe our approach to formal verification of the SRS component of a BLETC, and present the formal model and results.

@@

Our goal is to build a generic model of the SRS structure, and to prove that it satisfies its specification, that it calculates approximate running sums of received count values within acceptable error margins.
Let $\mathsf{RS}\;n$ denote, as in Figure~\ref{fig:srs}, output $n$ of the SRS structure, which is supposed to compute a sum of received count values, and let $\mathsf{true\_sum}\;n$ denote this sum.
The multi-layered structure of the SRS and the read delay of each shift register result in the outputs being delayed from the $\mathsf{true\_sum}$ values.
A sketch of the desired correctness statement is: \[\forall{n} \cdot \, \mathsf{RS}\;n= \mathsf{true\_sum}\; n \pm\text{acceptable error}\]
Although Figure~\ref{fig:srs} suggests that the SRS structure has only twelve outputs  (i.e. $0\leq{n}\leq11$), we obtain a more generic result (that is useful in future upgrades of the system) by proving the correctness of the above statement for all values of $n$.

@@

Prior to defining a formal model of the SRS and the theorems on the model, we developed an informal ``white board-level'' argument for why the SRS implements its intended behavior.
The essence of this argument relies on four facts which can be established from the structure of the SRS and some details about the timing relationship between layers:
\begin{enumerate}
\item The shift register of each slice (except the first) is updated once the content of the shift register of its previous slice is completely updated.
\item The integration window of a given shift register in a slice (except the first slice) can be decomposed into a sequence of  non-overlapping consecutive segments, $S_1, S_2, \ldots, S_w$ (where $w$ is the width of the shift register) each of which is equal to the size of the integration window of the shift register of the previous slice.
\item After a period of initialization, the values stored in the shift register of a given slice (except the first) are the $w$ outputs of the previous slice, where $w$ is the width of the shift register of this slice.
\item After a period of initialization, the output of each slice is always equal to the sum of the contents of its shift register.
\end{enumerate}
